
# Separator slide {visibility="hidden"}

```{r}

filtered_data <- filter(nhsrl_data, my_name == glue::glue("{{name}}"))

```

## Another slide {.hidden}

::: {.columns}
::: {.column width=55%}

::: {.columns}
::: {.column width=75%}

## {{name}}

`r paste0(ifelse(filtered_data$twitter != "", filtered_data$twitter, "<br>"), ifelse(filtered_data$mastodon != "", paste0(" | ", filtered_data$mastodon), ""))`

:::

::: {.column width=25%}

```{r, echo=FALSE, results='asis'}
profile_link <- case_when(filtered_data$profile_pic != "" ~ filtered_data$profile_pic,
                          TRUE ~ "https://cdn.pixabay.com/photo/2015/10/05/22/37/blank-profile-picture-973460__480.png")

cat("
<center>    
![](", glue::glue(profile_link), "){width=80%}
</center>", sep = "")

```

:::
:::

### I use R in the NHS to...

`r filtered_data$sentence`

::: {.columns}
::: {.column width=33%}

### I use R for... 

```{r, fig.height=3, fig.width=3}

filtered_data %>%
  ggplot() +
  geom_bar(aes(x = 0,
               y = 100),
           stat = "identity",
           fill = "#BBB6D5") +
  geom_bar(aes(x = 0, y = percent_max),
           fill = "#1D90A1",
           stat = "identity") +
  geom_bar(aes(x = 0, y = percent_min),
           fill = "#BBB6D5",
           stat = "identity",
           alpha = 0.5) +
  coord_polar(theta = "y") +
  ggtext::geom_textbox(aes(x = -3, y = 0,
                       label = paste0(percent,
                                      "<span style='font-family:Nunito Sans;font-size:16pt'><br>of my work</span>")),
                       hjust = 0.5, vjust = 0.5,
                       halign = 0.5,
                       family = "Zilla Slab", size = 11,
                       box.colour = NA, fill = NA,
                       colour = "#1D90A1") +
  theme_void() +
  xlim(c(-3, 0.5))

```

:::

::: {.column width=66%}

### ... and have been using R for...

```{r, fig.height=2.5, fig.width=5}
nhsrl_data %>%
  ggplot() +
  geom_bar(aes(x = my_name,
               y = years_tidy),
           stat = "identity",
           fill = "#BBB6D5") +
  geom_bar(data = filtered_data,
           aes(x = my_name,
               y = years_tidy),
           stat = "identity",
           fill = "#1D90A1") +
  coord_flip() +
  ggtext::geom_textbox(data = filtered_data, 
                       aes(x = my_name, y = years_tidy,
                       label = paste0(years_tidy,
                                      " <span style='font-family:Nunito Sans;font-size:14pt'>years</span>"),
                       hjust = case_when(years_tidy < 3 ~ 0, TRUE ~ 1),
                             halign = case_when(years_tidy < 3 ~ 0, TRUE ~ 1),
                             colour = case_when(years_tidy < 3 ~ "#1D90A1", TRUE ~ "#FFFFFF")),
                       family = "Zilla Slab", size = 10,
                       box.colour = NA, fill = NA) +
  scale_colour_identity() +
  theme_void()
```

:::

:::

### If your work or the work of your team suddenly ceased tomorrow, what would be the consequences for the NHS?

`r filtered_data$consequences`

::: 
::: {.column width=13%}

::: 
::: {.column width=32%}
<div style='color:#FFFFFF'>

### What first drew you to R? {.light}

`r filtered_data$first_drew`

<br>

### What other tools do you use? {.light}

`r filtered_data$tools`

<br>


### What resources would you recommend to other R users? {.light}

`r filtered_data$resources`

<br>


### Tell me something surprising about yourself! {.light}

`r filtered_data$surprise`

</div>
:::
:::

